A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-11-12 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Added .gitignore files and started response for re-submission

\begin{letter}{Dr Masoud Jabbari \\
CEng MIMechE PMSAMPE AMACerS MInterPore \\
Lead Guest Editor for Special Issue: \\
Applied Mathematical Modelling \\
WMG, University of Warwick \\
Coventry, CV4 7AL}

>>>>

\begin{letter}{Dr. Masoud Jabbari \\
CEng MIMechE PMSAMPE AMACerS MInterPore \\
Lead Guest Editor for Special Issue: \\
Applied Mathematical Modelling \\
WMG, University of Warwick \\
Coventry, CV4 7AL}
